Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-21 WSSSPE3/report/wg_main_funding_spec_expert.tex
Section 5.2 and Section 5.3: No content change
Update link to international list of RSE groups curated by UKRSE.

To find more information about this group, or join it, see \url{http://www.rse.ac.uk/groups}.

>>>>

To see our list of international research software engineering groups so far
visit \url{http://www.rse.ac.uk/international}. For the UK groups, see
\url{http://www.rse.ac.uk/groups}. Too add your group to the list, please make a pull request to
\url{https://github.com/UKRSE/UKRSE.github.io/blob/master/international.md}
